Preparing the NHANES Data for the Replication of: Association between sleep duration on workdays and blood pressure in non‑overweight/obese population in NHANES: a public database research

### 2023-12-09 manuscript/paper.Rmd
update

---
title: "Preparing the NHANES Data for the Replication of: Association between sleep duration on workdays and blood pressure in non‑overweight/obese population in NHANES: a public database research"
thanks: "Replication files are available on the author's Github account (http://github.com/okutse/sleepBP). **Current version**: `r format(Sys.time(), '%B %d, %Y')`; **Corresponding author**: steven.v.miller@gmail.com."
subtitle: "Short title goes here!"
author:
- Amos Okutse, Brown University
- Second Author, Another Uni
- Graduate Student, Graduate School
abstract: "**Introduction:** Lorem ipsum dolor sit amet, consectetur adipiscing elit. Donec sit amet libero justo. Pellentesque eget nibh ex. Aliquam tincidunt egestas lectus id ullamcorper.

@@

# Introduction

@@

The outcome is

The trained and certified examiners used the standardized protocols and
calibrated equipment to get the blood pressure readings. Three
consecutive BP readings were acquired via ausculatory means. If a BP
measurement was not successfully completed, a fourth measurement was
implemented. The average of all available measures was used.

@@

Table goes here for the covariate distributional questions

@@

Model 1 Model 3, 4, 5

## Methods 1

## Methods 2

## Methods 3

@@

## Results 1

### Results 1a

>>>>

---
title: "Preparing the NHANES Data for the Replication of: Association between sleep duration on workdays and blood pressure in non‑overweight/obese population in NHANES: a public database research"
thanks: "Replication files are available on the author's Github account (http://github.com/okutse/sleepBP). **Current version**: `r format(Sys.time(), '%B %d, %Y')`"
subtitle: "Short title goes here!"
author:
- Amos Okutse, Brown University
- Second Author, Another Uni
- Graduate Student, Graduate School
abstract: "**Introduction:** Lorem ipsum dolor sit amet, consectetur adipiscing elit. Donec sit amet libero justo. Pellentesque eget nibh ex. Aliquam tincidunt egestas lectus id ullamcorper.

@@

```{r source-file, echo=FALSE, include=FALSE}
# source file 
source(file = "/Users/aokutse/Desktop/PhD/Fall 2023/PHP2601 Linear Models/ProjectFinal/data/scrip2.R")
```
# Introduction

@@

We defined our outcome as systolic and diastolic blood pressure. These variables are measured by trained examiners using standardized procedures. Given that systolic and diastolic blood pressure measurements are taken at least four times on an individual, our definition of these outcome is based on an average of the first three blood pressure measurements.

@@

In addition to the exposure and outcome variables, our analyses included the following as covariates: Race divided into four groups as Mexican American, white, black and other race. Alcohol consumption was grouped into drinking, no drinking, not recorded. Smoking status as smoking, not smoking, not recorded. Diabetes was defined as yes, no, borderline, or not recorded. Hypertension was defined as yes, no, or not
recorded. Snorting was defined as yes, no, and not recorded. US citizenship status was defined as citizen by birth or naturalization, don't know, not a citizen, or refused to answer. Education level was grouped into four categories including graduate studies, high school, less than grade 12 or some college. Additional covariates included marital status, gender, age, albumin, creatinine,hemoglobin, total cholesterol (TC), aspertate aminotransferase (AST), high-density lipoprotein (HDL), and body mass index (BMI). Details about these variables can be found at https://wwwn.cdc.gov/nchs/nhanes/search/default.aspx. Age, albumin, creatinine, hemoglobin, TC, AST, HDL, and BMI were analyzed as continuous variables whereas gender, alcohol consumption, diabetes, smoking,
race, hypertension, and snorting were analyzed as categorical variables. Table \@ref{tab:tabone} highlights the variable names and descriptions as utilized in this study.

```{r tabone, echo=FALSE}
tab.one <- kable(vars, caption = "Variable names and descriptions", 
                 format = "latex") %>% 
  kable_styling(latex_options = c("HOLD_position")) %>% 
  row_spec(c(0), bold = TRUE) %>% 
  column_spec(c(1, 2), bold = TRUE, width = "2cm") %>% 
  column_spec(3, width = "8cm")
tab.one
```

@@

@@

Table \@ref(tab:tabtwo) summarizes participant characteristics in the 2015 - 2018 NHANES survey cycles stratified by gender. Among the participants, the proportion of males and females were 44.81% (n = 1378) and 55.19% (n = 1509),
respectively. With ethnicity, the proportion of Mexican American, White and Black were 6.27%, 64.62% and
9.94%, respectively. Overall, the mean (SD) values for age, albumin, creatinine, SBP, DBP, hemoglobin, TC, AST,
HDL, BMI were 38.54 (17.72) years, 43.48 (3.58) g/L, 73.21 (19.73) umol/L, 115.33 (14.56) mmHg, 68.47 (10.08)
mmHg, 14.07(1.44)g/dL, 4.67 (1.01) mmol/L, 23.18 (13.01) IU/L, 1.59 (0.43) mmol/L, and 21.97(2.06) kg/m2,
respectively. Among the participants, 66.01% were consumed alcohol drinkers, 2.61% were diabetes, 3.16% were
hypertension, 6.72% have snort or stop breathing. 17.99% were smokers. Sleep duration was divided into three
groups, which were < 6 h, 6–8 h, ≥ 8 h, each with a proportion of 6.26%, 40.53%, 53.21%, respectively.

Male and female participants differed significantly on characteristics including

The univariate
analysis of potential confounding factors is shown in Table 2.

```{r tabtwo, echo=FALSE}
tabsum %>% 
  as_kable_extra(format = "latex", caption = "Unweighted summary characteristics of the participants in the NHANES 2015 - 2018 survey cycles stratified by gender.", digits = 2, longtable = T) %>% 
  kable_styling(latex_options = c("HOLD_position"))
```
